---
title: "BMW"
output:
  html_document: default
  pdf_document: default
date: "2026-04-12"
---

SectionA:

The analysis was conducted using the tidyverse package in R. The dataset was first imported using read_csv() and inspected with glimpse() to ensure correct data structure and variable types. The data was then grouped by Year and Region using group_by(), and key metrics were calculated using summarise(), including the average BEV share, total units sold, and total revenue. To visualize trends over time, ggplot2 was used to create a line chart with points, where Year was mapped to the x-axis, BEV share to the y-axis, and Region was represented by different colors. This approach enabled a clear comparison of BEV adoption trends across regions and facilitated the identification of growth patterns and regional differences.

```{r setup, include=FALSE}
library(tidyverse)
df <- read_csv("C:/Users/Fengxinyu/Downloads/bmw_global_sales_2018_2025.csv")
```


```{r question_a_trend}
bev_trend <- df %>%
  group_by(Year, Region) %>%
  summarise(
    BEV_Share = mean(BEV_Share),
    Units_Sold = sum(Units_Sold),
    Revenue = sum(Revenue_EUR),
    .groups = "drop"
  )

ggplot(bev_trend, aes(x = Year, y = BEV_Share, color = Region)) +
  geom_line(linewidth = 1.2) +
  geom_point() +
  labs(
    title = "BEV Share Growth Over Time by Region",
    y = "BEV Share"
  )
```